### 2017-09-21 icde/sec-alg.tex

\stitle{Block-wise algorithm~\twprscc}.  It takes as input a citation or venue graph $G$ and an iteration threshold $\epsilon$, and returns the TWPageRank vector of $G$.
Moreover, to process an \scc instead of the entire graph, the edges of the citation or venue graph $G(V, E)$ are partitioned into the sets $E_i$ and $E_a$ of edges inside and across \sccs  such that $E_i\cap E_a = \emptyset$ and $E = E_i \cup E_a$.  The update rule in Eq.~(\ref{eq-twpr-update})  is revised accordingly to treat $E_i$ and $E_a$ separately as follows.

@@

\begin{proofSketch}
We first prove that the sum of changes after another iteration from $PR$, \ie $||d M^T PR + (1-d)e/n-PR||_1$, is smaller than $\epsilon$, and then prove that $||PR^*-PR||_1$ is smaller than the sum of changes. %(see~\cite {ERank-full} for details). % since $\epsilon > ||PR^+-PR||_1 = ||d\cdot M^T \cdot (PR-PR^*)||_1 + ||PR-PR^*||_1$.
\end{proofSketch}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[tb!]
%\vspace{-2ex}
\begin{center}
\caption{\small Statistics of citation/venue graphs and Web graphs~\cite{LeskovecLDM09}}
\label{tab-batch}
%\begin{small}
\vspace{-.5ex}
\begin{tabular}{|c|c|c|c|c|}
\hline
 &   &  & \multicolumn{1}{c|}{\bf Largest }   & \multicolumn{1}{c|}{\bf \scc }    \\
\raisebox{1ex}[0pt]{\bf Graphs}      & \multicolumn{1}{c|}{\raisebox{1ex}[0pt]{\bf Nodes}} & \multicolumn{1}{c|}{\raisebox{1ex}[0pt]{\bf Edges}} &
\multicolumn{1}{c|}{\bf $|\scc|$} &  \multicolumn{1}{c|}{\bf edge ratio}    \\
\hline \hline
\aan  & 18,041/565 & 82.9K/22.5K &  20/18  & 0.9\%/2.8\%      \\  %\hline
\aminer  & 3.14M/56K & 14.3M/7.1M   & 23/1.5 &  1.6\%/2.1\%     \\ %\hline    % 1.5K = 1467
\magdata  & 127M/584K & 526M/162M & 351/10K & 0.1\%/1.8\%    \\ \hline
web-BS  &  685,230 & 7,600,595 & \multicolumn{1}{c|}{334,857} & \multicolumn{1}{c|}{59.51\%}\\  %\hline
web-G  & 875,713 & 5,105,039 & \multicolumn{1}{c|}{434,818} & \multicolumn{1}{c|}{66.98\%} \\  %\hline
\hline
\end{tabular}
%\end{small}
\end{center}
\vspace{-5ex}
\end{table}
%%%%%%%%%%%%%%%%%%%

@@

To verify this observation, we also collect the statistics of citation graphs, venue graphs and Web graphs (shown in Table~\ref{tab-batch}), where Web graphs are extracted from berkely.edu and stanford.edu domains in 2002 and from the Google programming contest in 2002, respectively~\cite{LeskovecLDM09}.
Due to the existence of the ``bow tie'' structure and the giant \scc in Web graphs~\cite{BroderKMRRSTW00}, the edge ratios $|E_i|/|E|$ are greater than 59\% for Web graphs. In contrast, the \sccs in citation and venue graphs are quite small as a result of the temporal order of citation, and $|E_i|/|E|$ is less than 3\% for all tested citation and venue graphs.
%
This specific structure in scholarly data has been ignored in the literature, and has a positive impact on computations. Taking $t=100$ for example, algorithm \twprscc needs to scan $3|E|$ and $4|E|$ edges on citation and venue graphs, respectively, but over $59|E|$ edges on Web graphs.

>>>>

\stitle{Block-wise algorithm~\twprscc}.  It takes as input a citation or venue graph $G$ and an iteration threshold $\epsilon$, and returns the TWPageRank vector of $G$.
To process an \scc instead of the entire graph, the edges of the citation or venue graph $G(V, E)$ are partitioned into the sets $E_i$ and $E_a$ of edges inside and across \sccs  such that $E_i\cap E_a = \emptyset$ and $E = E_i \cup E_a$.  The update rule in Eq.~(\ref{eq-twpr-update})  is revised accordingly to treat $E_i$ and $E_a$ separately as follows.

@@

\begin{proofSketch}
We first prove that the sum of changes after another iteration from $PR$, \ie $||d M^T PR + (1-d)e/n-PR||_1$, is smaller than $\epsilon$, and then prove that $||PR^*-PR||_1$ is smaller than the sum of changes computed earlier. %(see~\cite {ERank-full} for details). % since $\epsilon > ||PR^+-PR||_1 = ||d\cdot M^T \cdot (PR-PR^*)||_1 + ||PR-PR^*||_1$.
\end{proofSketch}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[tb!]
%\vspace{-2ex}
\begin{center}
\caption{\small Statistics of citation/venue graphs and Web graphs~\cite{LeskovecLDM09}}
\label{tab-batch}
%\begin{small}
%\vspace{-.5ex}
\begin{tabular}{|c|c|c|c|c|}
\hline
 &   &  & \multicolumn{1}{c|}{\bf Largest }   & \multicolumn{1}{c|}{\bf \scc }    \\
\raisebox{1ex}[0pt]{\bf Graphs}      & \multicolumn{1}{c|}{\raisebox{1ex}[0pt]{\bf Nodes}} & \multicolumn{1}{c|}{\raisebox{1ex}[0pt]{\bf Edges}} &
\multicolumn{1}{c|}{\bf $|\scc|$} &  \multicolumn{1}{c|}{\bf edge ratio}    \\
\hline \hline
\aan  & 18,041/565 & 82.9K/22.5K &  20/18  & 0.9\%/2.8\%      \\  %\hline
\aminer  & 3.14M/56K & 14.3M/7.1M   & 23/1.5 &  1.6\%/2.1\%     \\ %\hline    % 1.5K = 1467
\magdata  & 127M/584K & 526M/162M & 351/10K & 0.1\%/1.8\%    \\ \hline
web-BS  &  685,230 & 7,600,595 & \multicolumn{1}{c|}{334,857} & \multicolumn{1}{c|}{59.51\%}\\  %\hline
web-G  & 875,713 & 5,105,039 & \multicolumn{1}{c|}{434,818} & \multicolumn{1}{c|}{66.98\%} \\  %\hline
\hline
\end{tabular}
%\end{small}
\end{center}
\vspace{-5ex}
\end{table}
%%%%%%%%%%%%%%%%%%%

@@

To verify this observation, we also collect the statistics of citation graphs, venue graphs and Web graphs (illustrated in Table~\ref{tab-batch}), where Web graphs are extracted from berkely.edu and stanford.edu domains in 2002 and from the Google programming contest in 2002, respectively~\cite{LeskovecLDM09}.
Due to the existence of the ``bow tie'' structure and the giant \scc in Web graphs~\cite{BroderKMRRSTW00}, the edge ratios $|E_i|/|E|$ are greater than 59\% for Web graphs. In contrast, the \sccs in citation and venue graphs are quite small as a result of the temporal order of citations, and $|E_i|/|E|$ is less than 3\% for all tested citation and venue graphs.
%
This specific structure in scholarly data has been long ignored in the past literature, which indeed has a positive impact on computations. Taking $t=100$ for example, algorithm \twprscc needs to scan $3|E|$ and $4|E|$ edges on citation and venue graphs, respectively, but over $59|E|$ edges on Web graphs.

### 2017-09-21 icde/sec-exp.tex

To alleviate the issue of citation missing in \aminer, we added citations by title matching  based on \magdata, and the finally total number of citations is 14.26 million. These datasets were further cleaned by deleting self-citations and citations from old articles to new ones, which accounted for (0.1\%, 0.8\%, 0.4\%) of the total citations on (\aan, \aminer, \magdata), respectively.
%from old articles to more recent ones
%These datasets were further cleaned by detecting citation cycles and removing those edges violating the temporal order if any.

@@

\noindent
(2) \fcita assumes that scholarly articles with more citations are of higher importance.
%
However, the number of entire citations is obviously biased to old articles. Some work adopts the number of future citations~\cite{Wang13AAAI,Wang16TIST,Li08TSRanking}, which is also not appropriate since this only estimates future impacts of articles, not at the concerned time. For a fair ranking benchmark, we propose to use both past and future citations with the same period of time \wrt\ the concerned time, such that the number of citations within these two periods reveals the importance of articles at the concerned time.
%
We hence divided each dataset into two parts with a splitting (concerned) time such that (a) the data before the splitting time is used for ranking model, (b) the remaining part of data is used to collect future citations, and (c) the most recent part of the data for ranking model with the same time span as the future citations is used to collect past citations.
%
%
Moreover, articles in the same pair were required to be in similar research fields, by utilizing the Fields-Of-Study information on \magdata~\cite{Sinha15:MAG}, and published in the same year, similar to~\cite{Wang16TIST}.
We used all pairs (around 50,000) for \aan, and randomly chose 300,000 pairs for both \aminer and \magdata.

>>>>

To alleviate the issue of citation missing in \aminer, we added citations by title matching  based on \magdata, and finally the  total number of citations is 14.26 million. These datasets were further cleaned by deleting self-citations and citations from old articles to new ones, which accounted for (0.1\%, 0.8\%, 0.4\%) of the total citations on (\aan, \aminer, \magdata), respectively.
%from old articles to more recent ones
%These datasets were further cleaned by detecting citation cycles and removing those edges violating the temporal order if any.

@@

\noindent
(2) \fcita assumes that scholarly articles with more citations are of higher importance.
%
However, the number of entire citations is obviously biased to old articles. Some work adopts the number of future citations~\cite{Wang13AAAI,Wang16TIST,Li08TSRanking}, which is also not appropriate since this only estimates future impacts of articles, not at the concerned time. For a fair ranking benchmark, we propose to use both past and future citations with the same period of time \wrt\ the concerned time, such that the number of citations within these two periods reveals the importance of articles at the concerned time.
%
We hence divided each dataset into two parts with a splitting (concerned) time such that (a) the data before the splitting time is used for ranking model, (b) the remaining part of data is used to collect future citations, and (c) the most recent part of the data for ranking model with the same time span as the future citations is used to collect past citations.
%
%
Moreover, articles in the same pairs were required to be in similar research fields, by utilizing the Fields-Of-Study information on \magdata~\cite{Sinha15:MAG}, and published in the same years, similar to~\cite{Wang16TIST}.
We used all pairs (around 50,000) for \aan, and randomly chose 300,000 pairs for both \aminer and \magdata.

### 2017-09-21 icde/sec-incAlg.tex

\stitle{Auxiliary data structure maintenance}.
Two auxiliary data structures in the batch algorithm~\twprscc need to be maintained : (a) on the block-wise graph,  a mapping that, given a node of graph $G$, returns the index of the \scc to which it belongs, and (b) the topological order of the nodes in the block-wise graph.
%
Observe that these auxiliary data structures can be easily maintained as follows.

@@

%%%%%%%%%%%%%%%%%%%%%Algorithm
\begin{figure}[tb!]
%\vspace{2ex}
\begin{center}
{\small
\begin{minipage}{3.36in}
\myhrule \vspace{-1.5ex}
\mat{0ex}{
%%%%%%%%%%%%%%%%%%%
{\sl Input:\/} \= An update $\Delta$ = $\Delta V\cup\Delta E$, TWPageRank vector $PR$ of $G$,\\
\hspace{5ex}   and the  topological order $O$ of the block-wise graph $G'$.\\
{\sl Output:\/} TWPageRank vector $PR^+$ of the updated graph $G^+$. \\
\\
\bcc \hspace{1.5ex}\=  $G_C'$ := the block-wise graph of $G_C$; \\
%\ \  $E_{CB}'$ := edges from $G_C'$ to $G'$\\
\icc\> $\Delta O$ := topological order of $G_C'$; \ \ $O^+$ := $\Delta O/O$; \\
\icc\> label \sccs of $G_C$ as $C$ and \sccs of $G$ with outgoing edges \\ \hspace{2.5ex}  having  weight changes as $B$,  the remaining \sccs of $G$ as $A$\\
\icc\>  \For each node $v'$ following $O^+$ \Do\\
\icc\>\hspace{2.5ex}\= $scc$ := the corresponding \scc of $v'$; \\
%\icc\>\>\If impact weight of $(v,w)$ is changed where $v\in scc$ \Then \\
%\icc\>\>\hspace{3ex}\= label $scc$ as $B$;\\
%\icc\>\>\> label SCC $w'$ as $B$ such that $(v',w')\in E'$; \\
\icc\>\> \If $scc$ is labeled as $C$ \Then \\
\icc\>\>\hspace{3ex}\= update $PR^+(v)$ ($v\in scc$) following algorithm~\twprscc; \\
\icc\>\>\> label \scc $w'$ as $B$ with $w'\in G'$ and $(v', w')\in E^+{'}$;\\
\icc\>\> \Else \If $scc$ is labeled as $B$ \Then \\
\icc\>\>\> update $PR^+(v)$ where $v\in scc$ with Eq.~(\ref{eq-inc-prscc}) until the \\ \hspace{8ex}  sum of TWPageRank score changes is less than $\epsilon\cdot \frac{|scc|}{|V^+|}$; \\
\icc\>\>\> label \scc $w'$ as $B$ with $(v',w')\in E'$;\\
\icc\>\> \Else $PR^+(v)$:=$PR(v)\cdot {n}/{n^+}$ where $v\in scc$; \\
\icc\> \Return $PR^+$.
}
\vspace{-2.5ex} \myhrule
\end{minipage}
}
\end{center}
\vspace{-1ex}
\caption{\small Algorithm~\inctwprscc for incremental TWPageRank} \label{alg-inctwprscc}
\vspace{-3ex}
\end{figure}
%%%%%%%%%%%%Algorithm

@@

\begin{example} \label{eg-layer-dag}
Figure~\ref{fig-inc-division} illustrates an example of incremental TWPageRank computation. Consider an update $\Delta$ on the original graph $G$.
%
It is obvious that the update $\Delta$ has no impacts on the SCCs of $G$, and $O^+$ defined earlier is a valid topological order of $G^+{'}$.
%
The original graph $G$ is then partitioned into affected and unaffected areas, and subgraphs $G_A$, $G_B$ and $G_C$ are associated with node sets $V_A$, $V_B$ and $\Delta V$, respectively. Here edge weight on $(y, x)$ changes due to the change of the citation peak time of node $x$, and, hence, node $y$ as well as all nodes reachable from $y$ are included in $G_B$.
%
When updating the TWPageRank scores, following $O^+$, scores of nodes in $G_C$, $G_B$ and $G_A$ are computed by iterations from scratch, by iterations with Eq.~(\ref{eq-inc-prscc}) using the existing TWPageRank vector and by scaling, respectively.
\end{example}

@@

Observe that (a) a topological order of $G'_C$ can be computed in $O(|V_C|+|E_C|+|E_{CB}|)$ time,
(b) updating the TWPageRank scores of nodes in subgraphs $G_B$ and $G_C$ costs $O(|V_B\cup V_C|+|E_{B,a}\cup E_{C,a}\cup E_{CB}|)+t^+|E_{B,i}\cup E_{C,i}|)$ time, and , finally, (c) updating the scores of nodes in $G_A$ costs $O(|V_A|)$ time. From these, the following holds.

@@

By Propositions~\ref{prop-converg} \& \ref{lemma-inc-topo} and Theorem \ref{lemma-subgraphA}, one can easily verify the correctness of algorithm \inctwprscc.
%
Note that  a) algorithm \inctwprscc computes \sccs and derives the topological order based  on $\Delta$ only, instead of $G^{+}$,
b) it skips edges in $E_A\cup E_{AB}$ when updating the scores of nodes in $G_A$ and $G_B$, and
c) the number $t^+$ is very likely smaller than the number $t$ of \twprscc when updating scores of nodes in $G_B$.
%
All these make \inctwprscc faster than \twprscc even though they have very similar time complexity.
%, as will also been shown by the experimental study,

>>>>

\stitle{Auxiliary data structure maintenance}.
Two auxiliary data structures in the batch algorithm~\twprscc need to be maintained: (a) the block-wise graph and  a mapping that, given a node of graph $G$, returns the index of the \scc to which it belongs, and (b) the topological order of the nodes in the block-wise graph.
%
Observe that these auxiliary data structures can be easily maintained as follows.

@@

%%%%%%%%%%%%%%%%%%%%%Algorithm
\begin{figure}[tb!]
%\vspace{2ex}
\begin{center}
{\small
\begin{minipage}{3.36in}
\myhrule \vspace{-1.5ex}
\mat{0ex}{
%%%%%%%%%%%%%%%%%%%
{\sl Input:\/} \= An update $\Delta$ = $\Delta V\cup\Delta E$, TWPageRank vector $PR$ of $G$,\\
\hspace{5ex}   and the  topological order $O$ of the block-wise graph $G'$.\\
{\sl Output:\/} TWPageRank vector $PR^+$ of the updated graph $G^+$. \\
\\
\bcc \hspace{1.5ex}\=  $G_C'$ := the block-wise graph of $G_C$; \\
%\ \  $E_{CB}'$ := edges from $G_C'$ to $G'$\\
\icc\> $\Delta O$ := topological order of $G_C'$; \ \ $O^+$ := $\Delta O/O$; \\
\icc\> label \sccs of $G_C$ as $C$, \sccs of $G$ with outgoing edges having \\ \hspace{2.5ex}    weight changes as $B$, and the remaining \sccs of $G$ as $A$;\\
\icc\>  \For each node $v'$ following $O^+$ \Do\\
\icc\>\hspace{2.5ex}\= $scc$ := the corresponding \scc of $v'$; \\
%\icc\>\>\If impact weight of $(v,w)$ is changed where $v\in scc$ \Then \\
%\icc\>\>\hspace{3ex}\= label $scc$ as $B$;\\
%\icc\>\>\> label SCC $w'$ as $B$ such that $(v',w')\in E'$; \\
\icc\>\> \If $scc$ is labeled as $C$ \Then \\
\icc\>\>\hspace{3ex}\= update $PR^+(v)$ ($v\in scc$) following algorithm~\twprscc; \\
\icc\>\>\> label \scc $w'$ as $B$ with $w'\in G'$ and $(v', w')\in E^+{'}$;\\
\icc\>\> \Else \If $scc$ is labeled as $B$ \Then \\
\icc\>\>\> update $PR^+(v)$ where $v\in scc$ with Eq.~(\ref{eq-inc-prscc}) until the \\ \hspace{8ex}  sum of TWPageRank score changes is less than $\epsilon\cdot \frac{|scc|}{|V^+|}$; \\
\icc\>\>\> label \scc $w'$ as $B$ with $(v',w')\in E'$;\\
\icc\>\> \Else $PR^+(v)$:=$PR(v)\cdot {n}/{n^+}$ where $v\in scc$; \\
\icc\> \Return $PR^+$.
}
\vspace{-2.5ex} \myhrule
\end{minipage}
}
\end{center}
\vspace{-1ex}
\caption{\small Algorithm~\inctwprscc for incremental TWPageRank} \label{alg-inctwprscc}
\vspace{-3ex}
\end{figure}
%%%%%%%%%%%%Algorithm

@@

\begin{example} \label{eg-layer-dag}
Figure~\ref{fig-inc-division} illustrates an example of incremental TWPageRank computation. Consider an update $\Delta$ on the original graph $G$.
%
It is obvious that the update $\Delta$ has no impacts on the SCCs of $G$, and $O^+$ defined earlier is a valid topological order of $G^+{'}$.
%
The original graph $G$ is then partitioned into affected and unaffected areas, and subgraphs $G_A$, $G_B$ and $G_C$ are associated with node sets $V_A$, $V_B$ and $\Delta V$, respectively. Here edge weight on $(y, x)$ changes due to the change of the peak time of node $x$, and, hence, node $y$ as well as all nodes reachable from $y$ are included in $G_B$.
%
When updating the TWPageRank scores, following $O^+$, scores of nodes in $G_C$, $G_B$ and $G_A$ are computed by iterations from scratch, by iterations with Eq.~(\ref{eq-inc-prscc}) using the existing TWPageRank vector and by scaling, respectively.
\end{example}

@@

Observe that (a) a topological order of $G'_C$ can be computed in $O(|V_C|+|E_C|+|E_{CB}|)$ time,
(b) updating the TWPageRank scores of nodes in subgraphs $G_B$ and $G_C$ costs $O(|V_B\cup V_C|+|E_{B,a}\cup E_{C,a}\cup E_{CB}|)+t^+|E_{B,i}\cup E_{C,i}|)$ time, and, finally, (c) updating the scores of nodes in $G_A$ costs $O(|V_A|)$ time. From these, the following holds.

@@

By Propositions~\ref{prop-converg} \& \ref{lemma-inc-topo} and Theorem \ref{lemma-subgraphA}, one can easily verify the correctness of algorithm \inctwprscc.
%
Note that  (a) algorithm \inctwprscc computes \sccs and derives the topological order based  on $\Delta$ only, instead of $G^{+}$,
(b) it skips edges in $E_A\cup E_{AB}$ when updating the scores of nodes in $G_A$ and $G_B$, and
(c) the number $t^+$ is very likely smaller than the number $t$ of \twprscc when updating scores of nodes in $G_B$.
%
All these make \inctwprscc faster than \twprscc even though they have very similar time complexity.
%, as will also been shown by the experimental study,

### 2017-09-21 icde/sec-model.tex

\stitle{Time-Weighted PageRank (TWPageRank)}. Most previous work simply exploits temporal information in the form of exponential decay~\cite{Li08TSRanking,Wang13AAAI,sayyadi09,WalkerXKM07}. We rethink the usage of time information in terms of the impacts of scholarly articles.
Recall that articles are categorized  into six citation patterns featured by the time when the articles reach their citation peaks~\cite{Chakraborty15}: (a) {\em PeakInit} with the citation-count peak in the first five years (but not the first year) after publication, (b) {\em PeakMul} with distinct multiple peaks, (c) {\em PeakLate} with a single peak in at least five years after publication, (d) {\em MonDec} with monotonically decreasing citations, (e) {\em MonIncr} with monotonically increasing citations, and, (f) {\em Other} for articles whose average numbers of citations per year are less than 1. Though the number of citations is an indicator of the impacts of articles~\cite{WangSB13,Garfield471}, its impact is time-dependent and is not simply in the form of exponential decay.
In general, {\em the impact of an article tends to decay with time after the peak time only}. That is, the impacts of articles directly decay with time only for those in {\em MonDec}, and decay with time after the peak time for those in {\em PeakInit}, {\em PeakLate} and {\em PeakMul}, and do not decay for ones in {\em MonIncr} (which is rare).
%Otherwise, its impact is fixed as a constant number. %, since we argue that the increment of its citations during this period is mainly due to the increase of its popularity.
Also observe that {\em each individual article has its own peak time} as articles may reach their citation peaks in different patterns and time.
%using the peak year in Fig.~\ref{fig-citation} is not appropriate for all articles. On the contrary, we compute a peak year for each article.

@@

\begin{figure}
\centering
\includegraphics[scale=0.48]{fig/yearly-references.eps}
\vspace{-1ex}
\caption{\small Citation statistics of scholarly articles that reports the (logscale) percentage of the number of citations of each year \wrt\ the total number of citations  in  \aan, \aminer and \magdata, respectively.}
\label{fig-reference}
\vspace{-4ex}
\end{figure}

@@

For scholarly article ranking, $T_u$ is the publication time of article $u$ and $Peak_v$ should be ideally set to the time when article $v$ has the highest impacts. Basically, it could simply be the year when article $v$ obtains the largest number of citations. However, recent work reveals that the volume of scientific publications as well as the number of citations grow exponentially with time~\cite{Dong2017KDD,BornmannM15}. We also collect and report the citations statistics on three scholarly datasets in Fig.~\ref{fig-reference}, which verifies the exponential distribution. Hence, we adopt the {\em scaled} number of citations $\Psi_v^{(t)}=\Phi_v^{(t)} / \log Z^{(t)}$ such that $\Phi_v^{(t)}$ and $Z^{(t)}$ are the number of citations of article $v$ at year $t$ and the total number of references at year $t$, respectively. The peak time $Peak_v$ is the time that maximizes $\Psi_v^{(t)}$.
%(\aan, \aminer and \magdata)
% since scholarly data is dynamic and continuously growing
%, and the increased number of references of each article over time
%Recent work observes that the volume of scientific publications doubled every 12 years between 1900 and 2015~\cite{Dong2017KDD}. It is not surprising that the number of references also grows exponentially~\cite{BornmannM15}.

@@

A {\em citation graph} $G^c(V^c, E^c)$ is firstly constructed using the citation information such that (a) a node in $V^c$ denotes an article, (b) a directed edge $(u,v)$ in $E^c$ denotes that $u$ cites $v$, and (c) each node is associated with two types of time information: the publication year and the latest year having the largest number of citations.

@@

\begin{figure}[tb!]
\centering
%\includegraphics[scale=0.15]{fig/framework.eps}
\includegraphics[scale=0.16]{fig/framework-lite-2.eps}
\vspace{-1ex}
\caption{\small Ranking model \ensemblerank} \label{fig-rankmodel}
\vspace{-3ex}
\end{figure}

@@

A {\em venue graph} $G^v(V^v, E^v)$ is firstly constructed using the citation information among venues such that (a) a node in $V^v$ represents a venue in a specific year, (b) a direct edge $(s,t)$ in $E^v$ denotes that there exist articles published in venue (in a specific year) $s$ citing articles published in venue (in a specific year) $t$, and (c) we use the {\em impact weight} to denote the weight $w_v(s,t)$ from venues $s$ to $t$, which is the sum of the impact weights from articles published in $s$ to $t$, \ie

>>>>

\stitle{Time-Weighted PageRank (TWPageRank)}. Most previous work simply exploits temporal information in the form of exponential decay~\cite{Li08TSRanking,Wang13AAAI,sayyadi09,WalkerXKM07}. We rethink the usage of time information in terms of the impacts of scholarly articles.
Recall that articles are categorized  into six citation patterns featured by the time when the articles reach their citation peaks~\cite{Chakraborty15}: (a) {\em PeakInit} with the citation-count peak in the first five years (but not the first year) after publication, (b) {\em PeakMul} with distinct multiple peaks, (c) {\em PeakLate} with a single peak in at least five years after publication, (d) {\em MonDec} with monotonically decreasing citations, (e) {\em MonIncr} with monotonically increasing citations, and, (f) {\em Other} for articles whose average numbers of citations per year are less than 1. Though the number of citations is an indicator of the impact of articles~\cite{WangSB13,Garfield471}, its impact is time-dependent and is not simply in the form of exponential decay.
In general, {\em the impact of an article tends to decay with time after the peak time only}. That is, the impacts of articles directly decay with time only for those in {\em MonDec}, and decay with time after the peak time for those in {\em PeakInit}, {\em PeakLate} and {\em PeakMul}, and do not decay for ones in {\em MonIncr} (which is rare).
%Otherwise, its impact is fixed as a constant number. %, since we argue that the increment of its citations during this period is mainly due to the increase of its popularity.
Also observe that {\em each individual article has its own peak time} as articles may reach their citation peaks in different patterns and time.
%using the peak year in Fig.~\ref{fig-citation} is not appropriate for all articles. On the contrary, we compute a peak year for each article.

@@

\begin{figure}
\centering
\includegraphics[scale=0.48]{fig/yearly-references.eps}
\vspace{-1ex}
\caption{\small Citation statistics of scholarly articles that reports the (logscale) percentage of the number of citations of each year \wrt\ the total number of citations  in  \aan, \aminer and \magdata, respectively.}
\label{fig-reference}
\vspace{-3ex}
\end{figure}

@@

For scholarly article ranking, $T_u$ is the publication time of article $u$ and $Peak_v$ should be ideally set to the time when article $v$ has the highest impacts. Basically, it could simply be the year when article $v$ obtains the largest number of citations. However, recent work reveals that the volume of scientific publications as well as the number of citations grow exponentially with time~\cite{Dong2017KDD,BornmannM15}. We also collect and report the citations statistics on three scholarly datasets in Fig.~\ref{fig-reference}, which verifies the exponential distribution. Hence, we adopt the {\em scaled} number of citations $\Psi_v^{(t)}=\Phi_v^{(t)} / \log Z^{(t)}$ such that $\Phi_v^{(t)}$ and $Z^{(t)}$ are the number of citations of article $v$ at year $t$ and the total number of citations at year $t$, respectively. The peak time $Peak_v$ is the time that maximizes $\Psi_v^{(t)}$.
%(\aan, \aminer and \magdata)
% since scholarly data is dynamic and continuously growing
%, and the increased number of references of each article over time
%Recent work observes that the volume of scientific publications doubled every 12 years between 1900 and 2015~\cite{Dong2017KDD}. It is not surprising that the number of references also grows exponentially~\cite{BornmannM15}.

@@

A {\em citation graph} $G^c(V^c, E^c)$ is firstly constructed using the citation information such that (a) a node in $V^c$ denotes an article, (b) a directed edge $(u,v)$ in $E^c$ denotes that $u$ cites $v$, and (c) each node is associated with two types of time information: the publication year and the latest year having the largest (logscale) number of citations.

@@

\begin{figure}[tb!]
\centering
%\includegraphics[scale=0.15]{fig/framework.eps}
\includegraphics[scale=0.175]{fig/framework-lite-2.eps}
\vspace{-1ex}
\caption{\small Ranking model \ensemblerank} \label{fig-rankmodel}
\vspace{-3ex}
\end{figure}

@@

A {\em venue graph} $G^v(V^v, E^v)$ is firstly constructed using the citation information among venues such that (a) a node in $V^v$ represents a venue in a specific year, (b) a direct edge $(s,t)$ in $E^v$ denotes that there exist articles published in venue (in a specific year) $s$ citing articles published in venue (in a specific year) $t$, and (c) we use the {\em impact weight} $w_v(s,t)$ to denote the weight  from venues $s$ to $t$, which is the sum of the impact weights from articles published in $s$ to $t$, \ie
